\documentclass{article} % For LaTex2e
\usepackage{iclr2022_conference,times}
% Optional math commands from https://github.com/goodfeli/dlbook_notation.
\input{math_commands.tex}

%######## PHY293: Uncomment your submission name
\newcommand{\phyname}{ - Lab Report}
%\newcommand{\phyname}{Progress Report}
%\newcommand{\phyname}{Final Report}

%######## PHY293: Put your Group Number here
%\newcommand{\gpnumber}{40}

\usepackage{hyperref}
\usepackage{xcolor}
\usepackage[normalem]{ulem}
\usepackage{url}
\usepackage{graphicx}
\usepackage{placeins}
\usepackage{float}
\usepackage{tikz}
\usepackage{multicol}

%######## PHY293: Put your project Title here
\title{Real-Time Neural Signal Filtering via \\
Hodgkin-Huxley Simulation Models}

%######## PHY293: Put your names, student IDs and Emails here
\author{Karys Littlejohns\\
Student\# \\
karys.littlejohns@mail.utoronto.ca
\And
Peter Leong \\
Student\# 1010892955 \\
peter.leong@mail.utoronto.ca \\
\AND
}

% The \author macro works with any number of authors. There are two commands
% used to separate the names and addresses of multiple authors: \And and \AND.
%
% Using \And between authors leaves it to \LaTex{} to determine where to break
% the lines. Using \AND forces a linebreak at that point. So, if \LaTex{}
% puts 3 of 4 authors names on the first line, and the last on the second
% line, try using \AND instead of \And before the third author name.

\newcommand{\fix}{\marginpar{FIx}}
\newcommand{\new}{\marginpar{NEW}}

\iclrfinalcopy 
%######## PHY293: Document starts here
\begin{document}

\maketitle

\vspace{-6ex}

\begin{abstract}

----Total Pages: \pageref{last_page}
\end{abstract}

\vspace{2ex}

\begin{multicols}{2}

\section{Introduction}

\section{Bohr's Hydrogen Atom Theory}

Bohr's theory of the hydrogen an atom was an early model to include quantum concepts, namely: quantized energy levels.
More importantly, his model enabled him to derive a numerical formula for the Rydberg constant based on the three key postulates.
Firslty, within this model, electrons revolve in specific orbits around the nucleus as defined by their energy level.
Secondly, the angular momentum $L$ of an electron is also quantized and is given by the formula:

\[
L = M_{e}vr_{n} = n \frac{h}{2pi}
\]

where $m_{e}$ is the electron's mass, $r_{n}$ is the radius of the $n$th orbit, and $h$ is Planck's constant.
Lastly, electrons move between quantized energy levels whereby they produce a signle photon of light.
Using these postulates, Bohr derived the formula for the Rydberg constant using the $n$th level energy of an electron:

\[
E_n = -\frac{2\pi^2 m_e e^4}{(4\pi\epsilon_0)^2 h^2} \frac{1}{n^2} = -\frac{hc R_H}{n^2}
\]

The energy emitted by a photon during transition from $n_i$ to $n_f$ is then:

\[
E_{\text{photon}} = hc R_H \left( \frac{1}{n_f^2} - \frac{1}{n_i^2} \right) 
\]

We can thus derive the famous Rydberg formula given below:

\[
\frac{1}{\lambda} = R_H \left( \frac{1}{n_f^2} - \frac{1}{n_i^2} \right)
\]

Although Bohr made great strides in understanding the atomic model, there are several key limitations in his theory's application.
The greatest of which is that Bohr's model fails for anything other than a single-electron atom.
Further, his theory cannot explain the intensity of emission spectra nor why some spectral lines are split into two.

\section{Equipment \& Procedure}

To observe these phenomena, key equipment including a spectrometer and a sodium lamp were used.
Additionally, the Hartmann Relation method was used to tune and calibrate the experiment apparatus.
The subsequent outline the equipments' function, calibration and experimental procedures in further detail.

\subsection{Station Apparatus \& Instruments}

The Rydberg experiment station's primary apparatus is a triprism spectrometer capable of resolving to 0.1 nm.


\subsection{Calibration with the Hartmann Relation Method}

\subsection{identification of the Unknown Gas}

\subsection{The Rydberg Constant}

\subsection{Calculating the Separation of Spectral Lines in the Yellow Doublet of Sodium}

\section{Results \& Discussion}

\subsection{Vernier Scale Readings}

\subsection{Rydberg Constant Results}

\subsection{Unknown Gas Identification}

\subsection{Spectrometer Resolution via Sodium Spectrum}

\section{Conclusion}

\label{last_page}

\newpage
\bibliographystyle{iclr2022_conference}
\bibliography{PHY293_Proposal_Ref}

\end{multicols}
\end{document}